---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clust431

<!-- badges: start -->
<!-- badges: end -->

The goal of clust431, created by Nils, Ryuhei, and Scott, is to provide R users with a K-means algorithm to assign k-clusters to any set of numerical data. 
The `k-means()` function has the ability to use a K-means++ algorithm to assign the original k-centroids, or use random assignment
if `pca == FALSE`.

clust431 also provides R users with the `hier_clust()` function, which outputs cluster assignment based on Hierarchical Agglomerative Clustering. By default, the distance measurement used to calculate clustering assignments is `method = "euclidean"`, but the methods `"euclidean", "maximum", "manhattan", "canberra", "binary", "minkowski"` can be input.

## Installation

You can install the released version of clust431 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("clust431")
```

## Loading package

```{r}
#| warning: false
library(clust431)
```

## Information from k_means function

- Users are provided with the observations' cluster assignments, distance to their respective cluster centroid, centroid coordinates of each respective cluster centroid, number of iterations to achieve the same clustering assignment, and the total sum of squares of the observations to the mean centroid of that data set.

```{r}
k_means(iris, 3, pca = FALSE)
```

## Plot genereated from k_means function

```{r}
results <- k_means(iris, 3, pca = TRUE)
plot_clusterings(results$Clusterings)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

## Hierarchical Agglomerative Clustering

```{r}
hier_clust(iris)
```

